Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-12 tex/paper.tex
Add sentence to CNN section

%%%%%%%%% TITLE
\title{Convolutional neural nets for the MNIST digit dataset}

@@

We can construct a different way to use a hierarchical representation of an image for classification
by performing convolutions at different scales of images with sets of filters.
Convolutional Neural Nets (CNNs) use a combination of convolutional layers, which perform convolution
of an image with a set of filters, and pooling layers, which reduce the dimensionality of the output
of convolutional layers, to create this representation.
Pooling layers reduce dimensionality by taking the maximum value (max-pooling) or mean value
(mean-pooling) of a region of convolutional outputs.
This reduction of dimensionality is important because it helps reduce the number of parameters that
must be trained in the network, thus speeding up learning.

>>>>

%%%%%%%%% TITLE
\title{Convolutional Neural Nets for the MNIST Digit Dataset}

@@

We can construct a different way to use a hierarchical representation of an image for classification
by performing convolutions at different scales of images with sets of filters.
Convolutional Neural Nets (CNNs) use a combination of convolutional layers, which perform convolution
of an image with a set of filters, and pooling layers, which reduce the dimensionality of the output
of convolutional layers, to create this representation. Convolutional layers serve to share the filter weights
across the image and thus reduce the number of parameters that must be trained, while also providing
a certain degree of traslational equivariance.
Pooling layers reduce dimensionality by taking the maximum value (max-pooling) or mean value
(mean-pooling) of a region of convolutional outputs.
This reduction of dimensionality is important because it helps reduce the number of parameters that
must be trained in the network, thus speeding up learning.
